---
title: "Management Plan 2024 - example of biological analysis"
output:
  word_document: default
bibliography: references.bib
---

This document is a draft of the biological analysis needed to model the effects of fishing effort reduction scenarios on stock quantities. The methodology is demonstrated on the Thyrrenian Sea and on stock assessments done with the a4a stock assessment model.

To come: examples on other areas and application of forecasts to other stock assessment models (ss3 and spict).

## Methodology

Data (stock objects and reference points) are gathered from STECF EWG 23-09 [@stecf2023a]. All these stock assessments are based on models fitted on timeseries ending in 2021 and updated to 2022 based on deterministic catch projections.

Forecast settings are:

-   Forecasts start in 2023

-   F status quo ($F_{sq}$) is defined as the $F_{bar}$ observed in the last year of assessment (2022)

-   F weak ($F_{weak}$) is defined as $F_{bar}*Reduction_{weak}$, where $Reduction_{weak}$ is the lower $F_{01}/F_{sq}$ observed in the area.

-   2023 and 2024 are intermediate year (F = $F_{sq}$ for each scenario)

-   F reductions are only applied to italian trawlers

-   Scenarios are applied over the period 2025-2027

-   2028-2030 are maintained equal to F values for 2027

Stock objects setting used in forecast period are:

-   Biological quantities (rec, weigth, mat) used for forecast are the mean of 2019-2021.

-   Stock-Recruitment relation used is geomean

-   Stochastic forecasts are implemented by adding residuals to the expected recruitment (age 1)

-   Recruitment residuals \~ Lognormal($\mu$, $\sigma^2$), where $\mu$ =0 and $\sigma^2$ is the CV of the observed recruitment (entire time series)

Scenarios are:

-   F status quo ($F_{sq}$ fixed up to 2030)
-   Fmsy transition: $F_y = a_y* F_{sq} + (1-a_y) * F_{01}$, where a is a vector of linear decrease
-   F weak: $F_y = a_y* F_{sq} + (1-a_y) * F_{weak}$, where a is a vector of linear decrease. This scenario simulates the effect of implementing to all stocks the same % reduction needed to reach $F_{01}$ for the stock having the largest $F_{sq}/F_{01}$ in 2022
-   Gradual reduction, 3% per year: $F_{y+1} = F_{y} * 0.97$
-   Gradual reduction, 5% per year: $F_{y+1} = F_{y} * 0.95$

\newpage
```{r, include=F,warning=F, echo=FALSE, fig.width = 1,results = 'asis'}
library(tidyverse)
 
```

# Catch share

The catch information was gathered by FDI catch data publicly available at https://stecf.ec.europa.eu/data-dissemination/fdi_en

These data reports the annual landed weigth by fleet. We used averages of the period 2020-2022 to calculate the fleet share. Following table only reports those fleets having at least 1% of share. 

```{r, include=T,warning=F, echo=FALSE, fig.width = 1,results = 'asis'}

  # table
  x.table=readr::read_csv("C:/Users/e.armelloni/OneDrive/Lezioni/Lavoro/Altro/piano_gestione/data/catch_share_FDI.csv")
x.table$landings=round(x.table$landings)
x.table=x.table[,c('species', 'area','country', 'gear','landings', 'prop')]
  tab=kableExtra::kable(x.table,
                    caption = "Catch share by fleet",
                     align = "ccccc",
                    row.names = F, format="markdown")%>%
  kableExtra::kable_styling(full_width = FALSE, position = "center",
                            font_size = 7)
  
  
  print(tab)
 #tab=pander::pander(stf.kab,
 #                 caption = "Forecast results by scenario in 2030", split.table = Inf)
 #print(tab)


```

\newpage

```{r setup, include=FALSE}
library(stringr)
library(readxl)
pander::panderOptions('table.split.table', Inf)   # Disable table splitting in Word
pander::panderOptions('table.alignment.default', 'center')  # Center align columns by default

stocks_info <- read_excel("C:/Users/e.armelloni/OneDrive/Lezioni/Lavoro/Altro/piano_gestione/data/stocks_info.xlsx")
stocks_info=stocks_info[stocks_info$stock!='NEP_17_18',]
main.dir="C:/Users/e.armelloni/OneDrive/Lezioni/Lavoro/Altro/piano_gestione/results/plots"
plot.list=list.files(main.dir)

# define some common information
target.pics=c('_stk','_fwd','_fwd_stc')
captions <- c("Stock trajectory from most recent stock assessment", 
              "Deterministic forecast",
              "Stochastic forecast")
images.size=c(400,400,400)
header_level <- "##"
```

# Tirreno

```{r, include=T,warning=F, echo=FALSE, fig.width = 1,results = 'asis'}
#knitr::include_graphics(file.path(main.dir,x.folder,j.images), dpi = 300)
stock.tir=stocks_info[stocks_info$area=='Tirreno',]
target=stock.tir$stock
for(j in 1:length(target)){
#for(j in 1:1){
#cat('\n\\newpage\n')
cat(sprintf('%s %s\n\n', header_level, target[j]))
  #cat('some random introduction to this model')
  #x.images=list.files(path = file.path(main.dir,x.folder), pattern='.png')
  x.images= paste0(target[j],target.pics,'.png')
  target.pics.vec=paste(target.pics, collapse = "|")
  x.images=x.images[grep(target.pics.vec,x.images )]
  cap.table=paste0(target[j], ": Forecast results by scenario in 2030")
  for(i in 1:length(target.pics)){
    j.target=target.pics[i]
    j.images=x.images[grep(j.target, x.images)][1]
    if(j.images%in%plot.list==F){next}
    filename <- file.path(main.dir,j.images)
    file.caption=paste(target[j], captions[i])
    cat(sprintf('![%s](%s){width=%s}\n\n', file.caption, filename, images.size[i]))
  }
  # table
  x.table=read.csv(file.path(main.dir,'..','forecasts', paste0(target[j],'_summary.csv')))
  if(j==6){
  stf.kab=x.table[x.table$year==2030,c('scenario','tot_b',  'fbar','catch_tot', 'catch_ita_otb')]  
  tab=kableExtra::kable(stf.kab,
                    col.names = c('Scenario','Total biomass (tons)', 'Fbar', 'Total Catches (tons)',  'Catches from Italian trawlers (tons)'),
                    caption = "Forecast results by scenario in 2030",
                     align = "ccccc",
                    row.names = F, format="markdown")%>%
  kableExtra::kable_styling(full_width = FALSE, position = "center")
  }else{
  stf.kab=x.table[x.table$year==2030,c('scenario','ssb',  'fbar','catch_tot', 'catch_ita_otb')]  
  tab=kableExtra::kable(stf.kab,
                    col.names = c('Scenario','SSB (tons)', 'Fbar', 'Total Catches (tons)',  'Catches from Italian trawlers (tons)'),
                    caption = "Forecast results by scenario in 2030",
                     align = "ccccc",
                    row.names = F, format="markdown")%>%
  kableExtra::kable_styling(full_width = FALSE, position = "center",
                            font_size = 7)
  }
  
  print(tab)
 #tab=pander::pander(stf.kab,
 #                 caption = "Forecast results by scenario in 2030", split.table = Inf)
 #print(tab)
}

```

\newpage

# Adriatico

```{r, include=T,warning=F, echo=FALSE, fig.width = 1,results = 'asis'}
#knitr::include_graphics(file.path(main.dir,x.folder,j.images), dpi = 300)
stock.adr=stocks_info[stocks_info$area=='Adriatico',]
target=stock.adr$stock
for(j in 1:length(target)){
#for(j in 1:1){
#cat('\n\\newpage\n')
cat(sprintf('%s %s\n\n', header_level, target[j]))
  #cat('some random introduction to this model')
  #x.images=list.files(path = file.path(main.dir,x.folder), pattern='.png')
  x.images= paste0(target[j],target.pics,'.png')
  target.pics.vec=paste(target.pics, collapse = "|")
  x.images=x.images[grep(target.pics.vec,x.images )]
  cap.table=paste0(target[j], ": Forecast results by scenario in 2030")
  for(i in 1:length(target.pics)){
    j.target=target.pics[i]
    j.images=x.images[grep(j.target, x.images)][1]
    if(j.images%in%plot.list==F){next}
    filename <- file.path(main.dir,j.images)
    file.caption=paste(target[j], captions[i])
    cat(sprintf('![%s](%s){width=%s}\n\n', file.caption, filename, images.size[i]))
  }
  # table
  x.table=read.csv(file.path(main.dir,'..','forecasts', paste0(target[j],'_summary.csv')))
if(j==4){
  stf.kab=x.table[x.table$year==2030,c('scenario','tot_b',  'fbar','catch_tot', 'catch_ita_otb')]  
  tab=kableExtra::kable(stf.kab,
                    col.names = c('Scenario','Total biomass (tons)', 'Fbar', 'Total Catches (tons)',  'Catches from Italian trawlers (tons)'),
                    caption = "Forecast results by scenario in 2030",
                     align = "ccccc",
                    row.names = F, format="markdown")%>%
  kableExtra::kable_styling(full_width = FALSE, position = "center")
  }else{
  stf.kab=x.table[x.table$year==2030,c('scenario','ssb',  'fbar','catch_tot', 'catch_ita_otb')]  
  tab=kableExtra::kable(stf.kab,
                    col.names = c('Scenario','SSB (tons)', 'Fbar', 'Total Catches (tons)',  'Catches from Italian trawlers (tons)'),
                    caption = "Forecast results by scenario in 2030",
                     align = "ccccc",
                    row.names = F, format="markdown")%>%
  kableExtra::kable_styling(full_width = FALSE, position = "center",
                            font_size = 7)
  }
  print(tab)
 #tab=pander::pander(stf.kab,
 #                 caption = "Forecast results by scenario in 2030", split.table = Inf)
 #print(tab)
}

```

\newpage

# Ionio

```{r, include=T,warning=F, echo=FALSE, fig.width = 1,results = 'asis'}
#knitr::include_graphics(file.path(main.dir,x.folder,j.images), dpi = 300)
stock.ion=stocks_info[stocks_info$area=='Ionio',]
target=stock.ion$stock
for(j in 1:length(target)){
#for(j in 1:1){
#cat('\n\\newpage\n')
cat(sprintf('%s %s\n\n', header_level, target[j]))
  #cat('some random introduction to this model')
  #x.images=list.files(path = file.path(main.dir,x.folder), pattern='.png')
  x.images= paste0(target[j],target.pics,'.png')
  target.pics.vec=paste(target.pics, collapse = "|")
  x.images=x.images[grep(target.pics.vec,x.images )]
   cap.table=paste0(target[j], ": Forecast results by scenario in 2030")
  for(i in 1:length(target.pics)){
    j.target=target.pics[i]
    j.images=x.images[grep(j.target, x.images)][1]
    if(length(j.images)==0){next}
    filename <- file.path(main.dir,j.images)
    file.caption=paste(target[j], captions[i])
    cat(sprintf('![%s](%s){width=%s}\n\n', file.caption, filename, images.size[i]))
  }
  # table
  x.table=read.csv(file.path(main.dir,'..','forecasts', paste0(target[j],'_summary.csv')))
  stf.kab=x.table[x.table$year==2030,c('scenario','ssb',  'fbar','catch_tot', 'catch_ita_otb')]  
  tab=kableExtra::kable(stf.kab,
                    col.names = c('Scenario','SSB (tons)', 'Fbar', 'Total Catches (tons)',  'Catches from Italian trawlers (tons)'),
                    caption = "Forecast results by scenario in 2030",
                     align = "ccccc",
                    row.names = F, format="markdown")%>%
  kableExtra::kable_styling(full_width = FALSE, position = "center",
                            font_size = 7)
  print(tab)
 #tab=pander::pander(stf.kab,
 #                 caption = "Forecast results by scenario in 2030", split.table = Inf)
 #print(tab)
}

```

# References
